---
title: "pre_class_1_exercises"
author: "Aske Bredahl"
date: "7/7/2019"
output:   
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pre-class 1 Exercises

The warm-up for class will use the mtcars dataset which is always present in R.
The following code shows you how load the dataset

```{r load the data}
library(pacman)
pacman::p_load(pacman, tidyverse) #laod packages
? mtcars # what are the variables
cars <- mtcars %>% rownames_to_column(var = "type") # tranform to tibble
```


This a brief re-introduction to the tidyverse package in R

This is something we went through during 1st semester so you should be able to do it, however if the summer have been to harsh I recommend consulting R for data science chapter 5: https://r4ds.had.co.nz
```{r}
# Using mutate - convert miles per gallon to liters
cars <- mutate(cars, cars$mpg/3.7854)

# Using filter - find all the cars which have more that 4 gears and are automatic
morethan4 <- filter(cars, cars$gear>4 & cars$am == 0)
morethan4

# Using select - create a column dataframe with only miles pr. gallon, weight and number og gears



# Using arrange - What cars are most fuel efficient? (lowest miles pr. liter/gallon)
cars <- arrange(cars, desc(cars$mpg))

# Using Group_by and summarise - Find out how many cars have 3 gears, how many have 4 and how many have 5 (tip use n(), with summarise to count number of occurences)
bygear <- cars %>% group_by(gear) %>% summarise(n())


# If you haven't yet, solve the above task using pipe, they look like this '%>%' and can be read as 'then' e.g. the following lines:
mtcars %>% 
  mutate(number = 200) %>% 
  summarise(sum_num = sum(number)) %>% 
  mutate(n_row = sum_num / 200)
# can be read as 'take mtcars, 
  # THEN add a column called numbers which is equal to 200
  # THEN the summarise the using the sum of numbers 
  # THEN divide the sum of the number by 200 to get the number of rows

hist(cars$gear)
qqplot(cars$gear, cars$mpg)
barplot(cars$gear, cars$mpg)




#create some sort of plot plotting the data


#Stine was here
```


